### 2017-09-21 F44 - Zeemanspektroskopie/parts/bib.tex
finish first version

\begin{thebibliography}{9}

\bibitem{czerny.turner}
  \href{https://de.wikipedia.org/wiki/Monochromator#/media/File:Czerny-turner.png}{Czerny-Turner Spektrometer},
  Wikipedia,
  10.09.17

\bibitem{fp.booklet}
  \href{http://www.physi.uni-heidelberg.de/Einrichtungen/FP/anleitungen/F44.pdf}{Literaturwert des Bohrschen Magnetons},
  F44 Versuchsanleitung von FP-Server,
  20.06.17

\bibitem{nist.gov.cd}
  \href{https://physics.nist.gov/PhysRefData/Handbook/Tables/cadmiumtable2.htm}{Literaturwerte des Cadmium Spektrums},
  NIST,
  01.09.17

\end{thebibliography}